Feature selection in fault classification of rotating machinery

### 2024-03-23 iit-src/paper.tex
Remove ANC from thesis and compare accuracies in box plots

existence of standards
domain - time, frequency, time-frequency
feature extraction techniques
feature selection techniques
classification of faults
datasets: mafaulda, cwru, rotating shaft
Raw - KSB Cloud - BVS pumps
!!! CITE do not describe !!!

@@

@@

Custom dataset
1. Choice of machines (pic measurement places - two images and dots)
2. HW sensor + ESP32 + FW 60 s. recor
3. How measure (plan)
4. Signal processing
4. Labeling  / Labeling (use machine - split by type) 
5. Same as Mafaulda

@@

For mafaulda and custom (which classes - all or just one machine)
- 1 ks All features (2x subplots TD, FD)
	- Each subplot boxplot (k = 3,5,7)

@@

>>>>

existence of standards
domain - time, frequency, time-frequency
feature extraction techniques
feature selection techniques
classification of faults
datasets: mafaulda, cwru, rotating shaft
Raw - KSB Cloud - BVS pumps

# analytical - known bearing
Ball Pass Frequency Outer Race (BPFO)
Ball Pass Frequency Inner Race (BPFI)
Ball Spin Frequency (BSF)
Fundamental Train Frequency (FTF)
!!! CITE do not describe !!!

@@

1. Choose frequency precision (1 Hz at maximum)
2. 12 windows at minimum (n+1 half windows with overlap), Hann window with 50\% overlap, 2^14 - 2^15 windows, 5s recodings

@@

Custom dataset
1. Choice of machines (pic measurement places - two images and dots) - pumps according to standards + callibrated sensors
	- compressor is on housing
2. HW sensor + ESP32 + FW 60 s. recor
3. How measure (plan)
4. Signal processing
4. Labeling  / Labeling (use machine - split by type) 
5. Same as Mafaulda

@@

Whole serach space = For mafaulda and custom (which classes - all or just one machine)
- 1 ks All features (2x subplots TD, FD)
	- Each subplot boxplot (k = 3,5,7)

2 features - best models under 55\% accuracy in test set

@@

- In training set growing number of neighbors decreases accuracy - in testing set there is no effect (more neighbors more overtraining)
	- we choose k = 5
- Number of features increases accuracy
